Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-26 paper/paper.qmd
updated 3 data graph,choose 1

---
title: "Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption"
author: 
  - Irene Liu
thanks: "Code and data are available at: https://github.com/zilin1017/Toronto_annual_energy_consumption.git."
date: today
date-format: long
abstract: "This study examines the relationship between building size(GFA) and electricity consumption in Toronto's public facilities. Data from over 500 buildings, including schools,libraries, and hospitals, show a consistent positive correlation between GFA and eletricity usage. Larger facilities, particularly healthcare centers, demonstrate higher energy consumption per square meter. These results help inform efforts to improve energy management in Toronto’s public buildings."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Load necessary libraries
library(readxl)
library(ggplot2)
library(tidyverse)

@@

# 基于数据的分面调整，并移除不必要的元素
annual_energy_consumption_data_2021 %>%
  ggplot(aes(x = Area, y = kWh, color = City)) +
  geom_point(alpha = 0.5) + # 设置透明度以减少重叠的影响
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ City, scales = "free") + # 允许每个分面自由缩放，以适应各自的范围
  ggtitle("Electricity Usage vs Building Size by Facility Type") +
  xlab("Building Size (GFA in m²)") +
  ylab("Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),  # 去掉y轴的数字
    axis.ticks.y = element_blank(),  # 去掉y轴的刻度
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

# Load necessary libraries
library(readxl)
library(ggplot2)
library(dplyr)

@@

>>>>

---
title: "Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption"
author: 
  - Irene Liu
thanks: "Code and data are available at: https://github.com/zilin1017/Toronto_annual_energy_consumption.git."
date: today
date-format: long
abstract: "This study examines the relationship between building size(m²) and electricity consumption(kWh) in Toronto's public facilities. Data from over 500 buildings, including schools,libraries, and hospitals, show a consistent positive correlation between GFA and eletricity usage. Larger facilities, particularly healthcare centers, demonstrate higher energy consumption per square meter. These results help inform efforts to improve energy management in Toronto’s public buildings."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

### graph1 ##
# Load necessary libraries
library(readxl)
library(ggplot2)
library(tidyverse)

@@

# 基于数据的分面调整，并移除不必要的元素
annual_energy_consumption_data_2021 %>%
  ggplot(aes(x = Area, y = kWh, color = City)) +
  geom_point(alpha = 0.5) + # 设置透明度以减少重叠的影响
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~ City, scales = "free") + # 允许每个分面自由缩放，以适应各自的范围
  ggtitle("Electricity Usage vs Building Size by City") +
  xlab("Building Size (GFA in m²)") +
  ylab("Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),  # 去掉y轴的数字
    axis.ticks.y = element_blank(),  # 去掉y轴的刻度
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

###2##
# Load necessary libraries
library(readxl)
library(ggplot2)
library(dplyr)

@@

##graph3##

# 使用柱状图展示不同建筑类型的总用电量
ggplot(annual_energy_consumption_data_2021, aes(x = Property_Type, y = `Electricity Use - Grid Purchase (kWh)`, fill = Property_Type)) +
  geom_bar(stat = "identity") +
  ggtitle("Total Electricity Usage by Property Type") +
  xlab("Property Type") +
  ylab("Total Electricity Usage (kWh)") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, margin = margin(b = 45), size = 10),
    axis.text.y = element_blank(), # Remove y-axis numbers
    axis.ticks.y = element_blank(), # Remove y-axis ticks
    axis.text.x = element_text(angle = 65, hjust = 1, size=6),
    legend.key.size = unit(0.3, "cm"),
    legend.text = element_text(size = 5))
